### 2015-07-02 reports/paper/conclusion.tex
thesis update

\chapter{Conclusion}
In this thesis, we described and built an inexpensive, portable yet reasonably accurate sound localization system with two microphone arrays. We have analyzed different array architectures and showed that the localization accuracy varies with the array geometry and the location of the sound source (in terms of both the distance and the angle). In particular, regions close to the line connecting two microphones are generally more difficult to localize than regions close the line bisecting two microphones. This problem can be alleviated by employing multiple microphones that are placed at large distance from each other, but such arrangement affects the portability of the system. As a trade off between accuracy and portability, we demonstrated that a two array architecture achieves better accuracy compared to a single array system of similar size. By using cross-correlation output as the likelihood for different arrival time differences, each array generates a likelihood map for each possible location in the area. We demonstrated that by merging likelihood maps from the two arrays, we were able to achieve good localization accuracy (less than $3$ cm average error) in a local one meter by one meter region. Since two arrays generate their likelihood maps individually, this system does not require synchronized clock between the arrays, which made the overall system easier to design and more portable.

>>>>

\chapter{Conclusion}
In this thesis, we described and built an inexpensive, portable yet reasonably accurate sound localization system with two microphone arrays. We have analyzed different array architectures and showed that the localization accuracy varies with the array geometry and the location of the sound source (both in terms of the distance and the angle). In particular, regions close to the line connecting two microphones are generally more difficult to localize than regions close to the line bisecting two microphones. This problem can be alleviated by employing multiple microphones that are placed at large distance from each other, but such arrangement affects the portability of the system. As a trade off between accuracy and portability, we demonstrated that a two array architecture achieves better accuracy compared to a single array system of similar size. By using cross-correlation output as the likelihood estimate for different arrival time differences, each array generates a likelihood map for each possible location in the area. We demonstrated that by merging likelihood maps from the two arrays, we were able to achieve good localization accuracy (less than $3$ cm average error) in a local one meter by one meter region. Since two arrays generate their likelihood maps individually, this system does not require synchronized clock between the arrays, which made the overall system easier to design and more portable.

### 2015-07-02 reports/paper/introduction.tex
thesis update

In this work, we have built a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area. The purpose of our system is to give applications to designs that allow remote human computer interaction. To test the accuracy of our localization system, we perform acoustic localization experiments in an one meter by one meter area. The experiment area size is adequate for our purposes because human arm movement will generally be constrained in this area. Our experiment show that our system localizes both static and moving acoustic source with good accuracy in this area. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

@@

This system can also be used to in Augmented Reality (AR) applications. For example, the user can wear a music tag on one finger, and then the system would be able to track the user's finger movements. This particular setup can be used as a virtual mouse for wearable technologies such as Google Glass.

\section{Contribution}
The main contributions of the thesis are:
\begin{enumerate}
\item We provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. 
\item We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. 
\item We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. 
\end{enumerate}
As a fun demonstration of the technology, we also demonstrated that our system can be used as a tool for painting in space.

\section{Outline}
We first discussed in Chapter II prior relevant research and approaches in sound localization. We also discussed various ways of combining past localization estimates for movement tracking. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

In this work, we have built a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area. The purpose of our system is to give applications to designs that allow remote human computer interaction. To test the accuracy of our localization system, we perform acoustic localization experiments in an one meter by one meter area. The experiment area is adequate for our purposes because human arm movement will generally be constrained in this area. Our experiment show that our system localizes both static and moving acoustic source with good accuracy in this area. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

@@

This system can also be used in Augmented Reality (AR) applications. For example, the user can wear a music tag on one finger, and then the system would be able to track the user's finger movements. This particular setup can be used as a virtual mouse for wearable technologies such as Google Glass.

\section{Contribution}
The main contributions of this thesis are:
\begin{enumerate}
\item We provided a detailed simulation analyzing the impact of arriving time difference estimation on localization error. 
\item We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining portability. 
\item We implemented and built the proposed sound localization system and compared different state of the art methods for point localization and movement tracking. 
\end{enumerate}
As a fun showcase of our technology, we also demonstrated that our system can be used as a tool for painting in space.

\section{Outline}
We first discussed in Chapter II the relevant research and approaches developed for sound localization. We also discussed various ways of combining recent localization estimates for movement tracking. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with its hardware details. Then we explained the experiment details and discussed the corresponding results.
